Catchy Title Goes Here

### 2018-04-30 Paper/paper.tex
added paper subdirectory

\subsection{MCMC Sampler \label{subsec:MCMC}}
Given our set of model parameters and the definition of the likelihood in Eq.~\ref{eq:loglike}, we can generate samples of the posterior distributions of the model parameters using Markov chain Monte Carlo (MCMC) techniques. We use the \texttt{PTMCMC} sampler package in Python, which incorporates parallel tempering, differential evolution, and proposals along the eigenvectors of the covariance matrix. This sampler is described in detail in ~\cite{Arzoumanian2014}.

We must specify prior distributions on each of our model parameters before running. These are listed in Table~\ref{table:priors}. 
\begin{center}
\begin{tabular}{ c|c } 
Parameter & Prior \\
 \hline
 $\alpha_v$, $\alpha_f$ & cell2 \\ 
 $\beta_v$, $\beta_f$ & cell5 \\ 
 $\eta_v$, $\eta_f$& cell8 \\ 
 $\gamma$ & cell9 \\
 \hline
 \label{table:priors}
\end{tabular}
\end{center}

@@

\subsection{Comparing Data and Inference \label{subsec:Comp}}

\section{Results \label{sec:Results}}

\bibliographystyle{unsrt}
\bibliography{../master}

>>>>

\subsection{MCMC Sampler \label{subsec:MCMC}}
Given our set of model parameters and the definition of the likelihood in Eq.~\ref{eq:loglike}, we can generate samples of the posterior distributions of the model parameters using Markov chain Monte Carlo (MCMC) techniques. We use the \texttt{PTMCMC} sampler package in Python~\cite{PTMCMC}, which incorporates parallel tempering, differential evolution, and proposals along the eigenvectors of the covariance matrix. This sampler is described in detail in ~\cite{Arzoumanian2014}.

We must specify prior distributions on each of our model parameters before running. These are listed in Table~\ref{table:priors}. 
\begin{table}
\begin{center}
\begin{tabular}{ c|c }  
Parameter & Prior \\
 \hline
 $\alpha_v$, $\alpha_f$ & $\Gamma(2,500)$ \\ 
 $\beta_v$, $\beta_f$ &$ \Gamma(2,5)$ \\ 
 $\eta_v$, $\eta_f$&$ \Gamma(2,15)$ \\ 
 $\gamma$ & $\beta(16,5)$ \\
 \hline
\end{tabular}
\caption{Prior distributions for the seven model parameters. $\Gamma(a,b)$ is the gamma distribution with shape $a$ and scale $b$, and $\beta(c,d)$ is the $\beta$ distribution with shape parameters $c$ and $d$. \label{table:priors}}
\end{center}
\end{table}

@@

\subsection{Comparing Data and Inference \label{subsec:Comp}}
A standard approach for interpreting the results of Bayesian inference would be to inspect the posterior distributions for the model parameters. But the parameters of our model are not, in themselves, particularly interesting - it is the inferred seroprevalence, case distribution, and vaccination probability that we wish to compare with the data. To do this, we generate the posteriors on $\{\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v\}$ as described, and then draw from these posteriors to generate the seroprevalence, case, and vaccination curves as laid out in Sec.~\ref{subsec:CompetingRates}. Because the vaccine efficacy, $\gamma$, is of interest on its own, we also examine the posterior distributions on $\gamma$ in detail.

In order to assess the impact of different types of data (case, serology, and vaccination data) on our inferences, we run the MCMC package described in Sec.~\ref{subsec:MCMC} on the vaccination and case data alone, the serology and case data alone, and all three datasets together. The results of all of these analyses are discussed below.

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Results:
Simulation experiment ? illustrate for 10 levels of vaccine effectiveness:
	a) Does fitted model using vaccination and case data only recover the true seroprevalence?
	b) Need to show that it recovers the vaccination hazard as well
	c) show estimate of vaccine effectiveness
Figure 1 ? 3-panel figure illustrating those 3 points

\subsection{DRC Data \label{subsec:DRC}}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability 	
Figure 2 ? pairs plots for all provinces and two models

Figure 3 ? Fitted seroprevalence curves for all provinces (maintain province color scheme throughout all figures). Note that x-scale should be years (up to 20 at least), it doesn?t make much sense over 59m
	- could probably squeeze all 11 into a single figure if played out well

Figure 4 ? fitted hazard functions illustrating variation in vaccination and force of infection.  4-panel, vaccination and FOI hazards for fits with and without serology data. (Note that FOI hazard should be on an x-scale of years, it doesn?t make much sense over 59m)
	- discuss variation observed.  Where is vaccination timely, where is FOI highest

Figure 5 ? comparison of prioritization
	- maybe 2 panels showing the seroprevalence by X years and the estimated vaccine efficacy for case data only v. case plus serology data.

	ASIDE ? would be worth plotting something like maximum vaccination coverage vs. some summary measure of the FOI ? you would expect to see lower FOI in places with higher coverage. If this pattern exists, that would definitely be worth showing!  There might be other summaries of the vaccination hazard that are more informative ? e.g. that account for speed up uptake AND max coverage.

\section{Discussion \label{sec:Discussion}}
Discussion:

Application for estimating seroprevalence in settings where a sero-survey is not possible 
	? serosurvey may not be feasible to do frequently, but this allows us to use passively collected age-specific case incidence 
	? doing a very wide serosurvey may not be feasible, or practical, but case surveillance lets you see signal across a wide age range

What is the use of this?
	? estimating seroprevalence in the absence of surveys
	? effect size estimate for designing sero-surveys

Discuss the interpretation of the patterns seen in the DRC data 
	? which places have good vaccination, which have high transmission
	? As I recall, some provinces have very wide FOI hazards, indicating that some people are getting infected relatively late in life.  There are lots of possible reasons for this, so should give it some thought.  Could relatively low exposure, so some people are just not exposed until late in life.  Could also reflect inflow of internally displaced people (IDPs).  Speculation depends on the pattern.

Several things that we haven?t dealt with here, that we?ll need to at least acknowledge:
	- we haven?t dealt with the fact that incidence and vaccination are not stationary
	- we haven?t dealt with supplemental campaigns
	- these are all things that can be dealt with at least theoretically

Take-home message about merging serosurveillance and case-based surveillance

\bibliographystyle{unsrt}
\bibliography{master}
